---
title: "Wikipedia Hindi/English Page Exploration"
author: "Molly G Hickman"
date: "9/30/2019"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(WikipediR)
library(pageviews)
library(distill)
library(rmarkdown)
library(dplyr)

start = "2000010112"
end = "2019100112"

articles_eng = c("Kashmir conflict", "Article 370 of the Constitution of India", "Insurgency in Jammu and Kashmir")

articles_hin = c("कश्मीर_विवाद", "अनुच्छेद_३७०", "जम्मू_और_कश्मीर_में_विद्रोह")

articles_urd = c("آئین_ہند_کی_دفعہ_370", "مسئلہ_کشمیر")

```

## Page Content
Note: Hindi page content query executes fine, but when you try to create the report it errors out

```{r page content}
# English
ekashmir = page_content("en", "wikipedia", page_name = articles_eng[1])
earticle = page_content("en", "wikipedia", page_name = articles_eng[2])
einsurg = page_content("en", "wikipedia", page_name = articles_eng[3])

# Hindi
hkashmir = page_content("hi", "wikipedia", page_name = articles_hin[1])
harticle = page_content("hi", "wikipedia", page_name = articles_hin[2])
hinsurg = page_content("hi", "wikipedia", page_name = articles_hin[3])
                         
```

## Page Views - English
```{r pageviews all fields?}
ekash_pv = article_pageviews(start=start, end=end, article=articles_eng[1])

colnames(ekash_pv)

ekash_pv$agent

```


```{r pageviews Kashmir conflict english}

# Subset of columns, for all paginated tables
wantCols = names(ekash_pv) %in% c('project', 'language', 'article', 'date', 'views')
paged_table(ekash_pv[wantCols])
```

```{r pageviews Article 370 english}
e370_pv = article_pageviews(start=start, end=end, article=articles_eng[2])
paged_table(e370_pv[wantCols])
```


```{r pageviews Jammu and Kashmir english}
ejamm_pv = article_pageviews(start=start, end=end, article=articles_eng[3])
paged_table(ejamm_pv[wantCols])
```

```{r merge to one file for output - english}
a <- bind_rows(ekash_pv, e370_pv, ejamm_pv)
write.csv(a, "wiki_english_pageviews_2000_thru_Sep2019.csv")
```

## Hindi pageviews

```{r pageviews Kashmir conflict hindi}
hkash_pv = article_pageviews(project="hi.wikipedia", start=start, end=end, article=articles_hin[1])
hkash_pv$article <- articles_eng[1] # replace unicode nonsense with article name
paged_table(hkash_pv)
```

```{r pageviews Article 370 hindi}
h370_pv = article_pageviews(project="hi.wikipedia", start=start, end=end, article=articles_hin[2])
h370_pv$article <- articles_eng[2] # replace unicode nonsense with article name
paged_table(h370_pv[wantCols])
```

```{r pageviews Jammu and Kashmir hindi}
hjamm_pv = article_pageviews(project="hi.wikipedia", start=start, end=end, article=articles_hin[3])
hjamm_pv$article <- articles_eng[3] # replace unicode nonsense with article name
paged_table(hjamm_pv[wantCols])
```

```{r merge to one file for output - hindi}
b <- bind_rows(hkash_pv, h370_pv, hjamm_pv)
write.csv(b, "wiki_hindi_pageviews_2000_thru_Sep2019.csv")
```

## Urdu pageviews

```{r pageviews Kashmir Conflict urdu}
ukash_pv = article_pageviews(project="ur.wikipedia", start=start, end=end, article=articles_urd[1])
ukash_pv$article <- articles_eng[1] # replace unicode nonsense with article name
paged_table(ukash_pv)
```

```{r pageviews Article 370 urdu}
u370_pv = article_pageviews(project="ur.wikipedia", start=start, end=end, article=articles_urd[2])
u370_pv$article <- articles_eng[2] # replace unicode nonsense with article name
paged_table(u370_pv)
```

```{r merge to one file for output - urdu}
b <- bind_rows(ukash_pv, u370_pv)
write.csv(b, "wiki_urdu_pageviews_2000_thru_Sep2019.csv")
```

## TODO! In progress - Get last X changes to each page and extract unique editors

Usage error: Recent changes is only for stream of changes on ALL articles in a "project" ("wikipedia.org" is a "project"). Maybe it's time to switch over to Python.

```{r get changes - english... and hindi?}

changesListEng <- lapply(articles_eng, FUN = function(article) {
  recent_changes(language="en", project=article, domain="wikipedia.org", properties=c("user", "userid", "comment", "parsedcomment", "flags","timestamp", "title"), limit=10, clean_response = TRUE)
}) 

changesListHin <- lapply(articles_hin, FUN = function(article) {
  recent_changes(language="hi", project=article, domain="wikipedia.org", properties=c("user", "userid", "comment", "parsedcomment", "flags","timestamp", "title"), limit=10, clean_response = TRUE)
}) 

changes_one <- recent_changes(language="en", project=articles_eng[1], domain="wikipedia.org", properties=c("user", "userid", "comment", "parsedcomment", "flags","timestamp", "title"), limit=10, clean_response = TRUE)

```


```{r unique editors}
df <- as.data.frame(changesListEng[1])

df1 <- as.data.frame(changes_one)
```

